---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OpenAIRE

<!-- badges: start -->
[![R-CMD-check](https://github.com/KTH-Library/OpenAIRE/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/KTH-Library/OpenAIRE/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

OpenAIRE is an open science initiative, which supports the Open Access policy of the European Commission. This R package `OpenAIRE` provides access from within R to the OpenAIRE RESTful APIs, which are intended for metadata discovery and exploration only.

## Installation

You can install the development version of OpenAIRE like so:

``` r
# install.packages("devtools")
devtools::install_github("KTH-Library/OpenAIRE")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(OpenAIRE)

openaire_projects()

```
